### 2016-09-01 lineups.Rnw
anon'd tables

\begin{figure}
\begin{subfigure}[t]{.45\textwidth}
\caption{Example 1}
\includegraphics[width=\textwidth]{Ex1}
\end{subfigure}\hfill
\begin{subfigure}[t]{.45\textwidth}
\caption{Example 2}
\includegraphics[width=\textwidth]{Ex2}
\end{subfigure}
\caption{\label{fig:lineupex} The first training page in the Amazon Turk experiment.}
\end{figure}

\begin{figure}
\begin{subfigure}[t]{.45\textwidth}
\caption{Trial 1}
\includegraphics[width=\textwidth]{Trial1}
\end{subfigure}\hfill
\begin{subfigure}[t]{.45\textwidth}
\caption{Trial 2}
\includegraphics[width=\textwidth]{Trial2}
\end{subfigure}
\caption{\label{fig:lineuptrial} The trial plots that users had to get correct in order to participate in the Amazon Turk experiment.}
\end{figure}

@@

<<get_res, echo=FALSE, warning=FALSE, message=FALSE, fig.align="center", fig.cap="Boxplot showing the percent of users correctly choosing the alternative model in all 25 lineups. In 15 out of 25 lineups, no user picked the correct plot. The maximum was 64.00\\%, and the second highest was 35.29\\% correct.", fig.height=3>>=
ids <- readr::read_csv("https://raw.githubusercontent.com/erichare/lineups/f19635a00507210013ba9e631761ad0c89a6564d/experiments/turk21/details/picture-details.csv")
tab <- read.csv("../Results/turk21_users.csv")
tab2 <- unique(tab)
#length(unique(tab2$nick_name))
#head(sort(table(tab2$nick_name),decreasing = T))
#tab2 %>% filter(nick_name == "A3U3L1XQVR362A")
#tab2 %>% filter(nick_name == "ADTIO3A6TM9CG")
#tab2 %>% filter(nick_name %in% names(table(res$nick_name))[table(res$nick_name) != 10])
res <- read.csv("../Results/turk21_feedback.csv", stringsAsFactors = F)
# remove people who only completed 1 plot
res <- res %>% filter(!(nick_name %in% names(table(res$nick_name))[table(res$nick_name) != 10]))
# need to repeat rows with weights for people who selected multiple plots.
res_norpt <- res[-grep(",", res$response_no),]  
res_rpt <- res[grep(",", res$response_no),]  
res_rpt$response_no
library(stringr)
# count # of responses (ttr = times to repeat)
ttr <- str_count(string = res_rpt$response_no, pattern = ",") + 1
rpt_rows <- rep(1:nrow(res_rpt), ttr)
rpt_rows2 <- res_rpt[rpt_rows,]
rpt_rows2$count_response <- unlist(sapply(ttr, seq_len))
rpt_rows2$weight <- 1/rep(ttr, ttr)
split_rows <- strsplit(rpt_rows2$response_no, ",")
rpt_rows2$response_no2 <- NA
for(i in 1:nrow(rpt_rows2)){
  rpt_rows2$response_no2[i] <- split_rows[[i]][rpt_rows2$count_response[i]]
}

@@

\begin{figure}
\begin{subfigure}[c]{.45\textwidth}
\textbf{Gender:} \\
<<tab_demo, echo=FALSE, results='asis'>>=
t1 <- t(data.frame(table(tab2$gender)))
rownames(t1) <- c("Gender:", "Count:")
colnames(t1) <- t1[1,]
t1 <- t1[2,]
kable(t1, format = 'latex')
@
\vspace{.5cm}
\textbf{Education Level:} \\
<<tab_demo3, echo=FALSE, results='asis'>>=
t3 <- t(data.frame(table(tab2$academic_study)))
rownames(t3) <- c("Highest Education:", "Count:")
colnames(t3) <- t3[1,]
t3 <- t3[2,]
kable(t3, format = 'latex')
@
\end{subfigure}\hfill
\begin{subfigure}[c]{.45\textwidth}
\centering
\textbf{Age Group:} \\
<<tab_demo2, echo=FALSE, results='asis'>>=
t2 <- t(data.frame(table(tab2$age)))
rownames(t2) <- c("Age:", "Count:")
colnames(t2) <- t2[1,]
t2 <- t2[2,]
kable(t2, format = 'latex')
@
\end{subfigure}
\caption{\label{fig:demos} Demographic information on the Amazon Turk users participating in the experiment}
\end{figure}

>>>>

\begin{figure}
\begin{subfigure}[t]{.45\textwidth}
\caption{Example 1}
\includegraphics[width=\textwidth]{Results/Ex1}
\end{subfigure}\hfill
\begin{subfigure}[t]{.45\textwidth}
\caption{Example 2}
\includegraphics[width=\textwidth]{Results/Ex2}
\end{subfigure}
\caption{\label{fig:lineupex} The first training page in the Amazon Turk experiment.}
\end{figure}

\begin{figure}
\begin{subfigure}[t]{.45\textwidth}
\caption{Trial 1}
\includegraphics[width=\textwidth]{Results/Trial1}
\end{subfigure}\hfill
\begin{subfigure}[t]{.45\textwidth}
\caption{Trial 2}
\includegraphics[width=\textwidth]{Results/Trial2}
\end{subfigure}
\caption{\label{fig:lineuptrial} The trial plots that users had to get correct in order to participate in the Amazon Turk experiment.}
\end{figure}

@@

<<get_res, echo=FALSE, warning=FALSE, message=FALSE, fig.align="center", fig.cap="Boxplot showing the percent of users correctly choosing the alternative model in all 25 lineups. In 15 out of 25 lineups, no user picked the correct plot. The maximum was 64.00\\%, and the second highest was 35.29\\% correct.", fig.height=3>>=
ids <- readr::read_csv("https://raw.githubusercontent.com/erichare/lineups/f19635a00507210013ba9e631761ad0c89a6564d/experiments/turk21/details/picture-details.csv")
tab <- read.csv("Results/turk21_users.csv")
tab2 <- unique(tab)
#length(unique(tab2$nick_name))
#head(sort(table(tab2$nick_name),decreasing = T))
#tab2 %>% filter(nick_name == "A3U3L1XQVR362A")
#tab2 %>% filter(nick_name == "ADTIO3A6TM9CG")
#tab2 %>% filter(nick_name %in% names(table(res$nick_name))[table(res$nick_name) != 10])
res <- read.csv("Results/turk21_feedback.csv", stringsAsFactors = F)
# remove people who only completed 1 plot
res <- res %>% filter(!(nick_name %in% names(table(res$nick_name))[table(res$nick_name) != 10]))
# need to repeat rows with weights for people who selected multiple plots.
res_norpt <- res[-grep(",", res$response_no),]  
res_rpt <- res[grep(",", res$response_no),]  
res_rpt$response_no
library(stringr)
# count # of responses (ttr = times to repeat)
ttr <- str_count(string = res_rpt$response_no, pattern = ",") + 1
rpt_rows <- rep(1:nrow(res_rpt), ttr)
rpt_rows2 <- res_rpt[rpt_rows,]
rpt_rows2$count_response <- unlist(sapply(ttr, seq_len))
rpt_rows2$weight <- 1/rep(ttr, ttr)
split_rows <- strsplit(rpt_rows2$response_no, ",")
rpt_rows2$response_no2 <- NA
for(i in 1:nrow(rpt_rows2)){
  rpt_rows2$response_no2[i] <- split_rows[[i]][rpt_rows2$count_response[i]]
}

@@

\begin{figure}
\begin{subfigure}[c]{.45\textwidth}
\textbf{Gender:} \\
<<tab_demo, echo=FALSE, results='asis'>>=
t1 <- t(data.frame(table(tab2$gender)))
rownames(t1) <- c("Gender:", "Count:")
colnames(t1) <- t1[1,]
t1 <- t1[2,]
t1[as.numeric(t1) < 5] <- "*"
kable(t1, format = 'latex')
@
\vspace{.5cm}
\textbf{Education Level:} \\
<<tab_demo3, echo=FALSE, results='asis'>>=
t3 <- t(data.frame(table(tab2$academic_study)))
rownames(t3) <- c("Highest Education:", "Count:")
colnames(t3) <- t3[1,]
t3 <- t3[2,]
t3[as.numeric(t3) < 5] <- "*"
kable(t3, format = 'latex')
@
\end{subfigure}\hfill
\begin{subfigure}[c]{.45\textwidth}
\centering
\textbf{Age Group:} \\
<<tab_demo2, echo=FALSE, results='asis'>>=
t2 <- t(data.frame(table(tab2$age)))
rownames(t2) <- c("Age:", "Count:")
colnames(t2) <- t2[1,]
t2 <- t2[2,]
names(t2)
t2.2 <- t2
t2.2 <- t2.2[1:7]
names(t2.2)[6:7] <- c("46-55", "Over 55")
t2.2[6:7] <- c(sum(as.numeric(t2[6:7])), sum(as.numeric(t2[8:9])))
kable(t2, format = 'latex')
@
\end{subfigure}
\caption{\label{fig:demos} Demographic information on the Amazon Turk users participating in the experiment. Asterisks (*) indicate less than 5 responses.}
\end{figure}
